Symbiont shuffling linked to differential photochemical efficiency of *Symbiodinium* in three Caribbean reef corals

### 2017-06-19 analysis/analysis.Rmd
fix Fig4 colors

plot(df$shuffle ~ df$ADH.days, ylim=c(-1,1), yaxs="r", xpd=NA,
     pch=c(16,15,17)[as.numeric(as.factor(df$BleachLvl))],
     xlab=expression("A"["Heat"]^"D"~"x (Days of heat stress)"),
     ylab="", mgp=c(1.8,0.1,0),
     col=c("#d95f02", "#1b9e77", "#7570b3")[as.numeric(factor(df$Species))])
mtext("Symbiont shuffling", side=2, line=1.5)
mtext("B.", adj=-0.2, font=2)
lines(seq(0,3,0.1), rescale(predicted, from=c(0,1), to=c(-1,1)), lwd=1)
abline(h=0, lwd=0.5)
text(par("usr")[2]*0.95, c(0.08, -0.1), pos=2, cex=0.7,
     labels=c("more clade D", "less clade D"))
arrows(par("usr")[2]*0.95, c(0.02, -0.02), 
       par("usr")[2]*0.95, c(0.2, -0.2), length=0.1)
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       pch=c(15, 17, 16), col="black", cex=0.7,
       legend=c("7 days", "10 days", "14 days"))
dev.off()
```
![Figure 4. Symbiont shuffling as a function of the photochemical advantage of clade D and heat stress duration. Panel **(A)** shows the symbiont shuffling response (as in Fig. 3B) as a function of heat stress duration (days) and the photochemical advantage of clade D under heat stress (A^D^~Heat~), with lines corresponding to the A^D^~Heat~ values for the three coral species studied (indicated by color), and two hypothetical intermediate values (gray lines). Panel **(B)** shows that the symbiont shuffling responses observed across all three species are predicted well (psuedo-R^2^=0.93) by the time-integrated photochemical advantage of clade D under heat stress.](../figures/Fig4.png)

>>>>

plot(df$shuffle ~ df$ADH.days, ylim=c(-1,1), yaxs="r", xpd=NA,
     pch=c(16,15,17)[as.numeric(as.factor(df$BleachLvl))],
     xlab=expression("A"["Heat"]^"D"~"x (Days of heat stress)"),
     ylab="", mgp=c(1.8,0.1,0),
     col=c("#1b9e77", "#7570b3", "#d95f02")[as.numeric(factor(df$Species))])
mtext("Symbiont shuffling", side=2, line=1.5)
mtext("B.", adj=-0.2, font=2)
lines(seq(0,3,0.1), rescale(predicted, from=c(0,1), to=c(-1,1)), lwd=1)
abline(h=0, lwd=0.5)
text(par("usr")[2]*0.95, c(0.08, -0.1), pos=2, cex=0.7,
     labels=c("more clade D", "less clade D"))
arrows(par("usr")[2]*0.95, c(0.02, -0.02), 
       par("usr")[2]*0.95, c(0.2, -0.2), length=0.1)
legend("bottomright", bty="n", inset=c(0.05, 0.1),
       pch=c(15, 17, 16), col="black", cex=0.7,
       legend=c("7 days", "10 days", "14 days"))
dev.off()
```
![Figure 4. Symbiont shuffling as a function of the photochemical advantage of clade D and heat stress duration. Panel **(A)** shows the symbiont shuffling response (as in Fig. 3B) as a function of heat stress duration (days) and the photochemical advantage of clade D under heat stress (A^D^~Heat~), with lines corresponding to the A^D^~Heat~ values for the three coral species studied (indicated by color), and two hypothetical intermediate values (gray lines). Panel **(B)** shows that the symbiont shuffling responses observed across all three species are predicted well (psuedo-R^2^=0.93) by the time-integrated photochemical advantage of clade D under heat stress.](../figures/Fig4.png)
